Title of the Project

### 2024-11-06 Report_Template.Rmd
initial template

---
title: "Gillespie algorithm for simulating stochastic equations of molecular reactions"
author: "First  Last Name"
date: "`r Sys.Date()`" #  
output:
  pdf_document:
      number_sections: true
spacing: double
header-includes:
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancyhead[L]{Title of Project}
- \fancyfoot[CO,CE]{}
- \fancyfoot[LE,RO]{\thepage}
- \usepackage{setspace}\doublespacing
---

```{=tex}
\newpage 
\tableofcontents 
\newpage
```

@@

Section 2: original algorithm and basic theory
Section 3: modified algorithm
Section 4: example
Section 5: conclusion (how the modification is better, when to use)

@@

# References
"Lu, Ting, et al. Cellular growth and division in the Gillespie algorithm. Systems biology 1.1 (2004):
121-128."

>>>>

---
title: "Title of the Project"
author: "First  Last Name"
date: "`r Sys.Date()`" # or DEcember 1, 2023
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    toc: yes
---

@@

@@

# References
